# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data

```{r echo=TRUE}
#Read the "activity.csv" file, from the "activity.zip" file, which I unzipped and placed in the same directory as the Rmarkdown file. By the way, this folder is also my working directory, which is previously set.

data <- read.csv("activity.csv", header = TRUE, sep = ",", na.strings="NA",
                 colClass=c("numeric","Date","numeric"))
```

## What is mean total number of steps taken per day?

# Make a histogram of the total number of steps taken each day (ignore the missing values)
# Calculate and report the mean and median total number of steps taken per day

```{r echo=TRUE}
#Create a new dataset without the missing values
dataclean = data[!is.na(data$steps), ]
#Aggregate this new dataset by sum of steps on each day
sumStep = aggregate(steps~date, dataclean, sum)
#Plot the number of steps
hist(sumStep$steps, col ="pink", main="Total number of steps taken each day", xlab="Number of steps each day")
#Calculate the mean and reporte the value
mean = mean(sumStep$steps)
mean
## [1] 10766.19
#Calculate the median and reporte the value
median = median(sumStep$steps)
median
## [1] 10765
```

## What is the average daily activity pattern?
# Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r echo = TRUE}
#Aggregate the dataset without the missing values by mean of steps for each interval
meanStep = aggregate(steps~interval, dataclean, FUN="mean")
#Plot the intervals on the x-axis and the averaged steps on the y-axis
plot(meanStep$interval, meanStep$steps, type = "l", col = "pink",
     main = "Average number of steps on each interval",
     xlab = "5-minutes intervals",
     ylab = "averaged steps")

```
#Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r echo=TRUE}
max.steps <- meanStep[which.max(meanStep$steps),1]
max.steps
##[1] 835
```


## Imputing missing values
# Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)



## Are there differences in activity patterns between weekdays and weekends?
