# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data

```{r echo=TRUE}
#Read the "activity.csv" file, from the "activity.zip" file, which I unzipped and placed in the same directory as the Rmarkdown file. By the way, this folder is also my working directory, which is previously set.

data <- read.csv("activity.csv", header = TRUE, sep = ",", na.strings="NA",
                 colClass=c("numeric","Date","numeric"))
```

## What is mean total number of steps taken per day?

# Make a histogram of the total number of steps taken each day (ignore the missing values)
# Calculate and report the mean and median total number of steps taken per day

```{r echo=TRUE}
#Create a new dataset without the missing values
dataclean = data[!is.na(data$steps), ]
#Aggregate this new dataset by steps
sumStep = aggregate(steps~date, dataclean, sum)
#Plot the number of steps
hist(sumStep$steps, col ="pink", main="Total number of steps taken each day", xlab="Number of steps each day")
#Calculate the mean and reporte the value
mean = mean(sumStep$steps)
mean
## [1] 10766.19
#Calculate the median and reporte the value
median = median(sumStep$steps)
median
## [1] 10765
```

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
